\sysfull

### 2018-04-16 paper/background.tex
fine-tuning of background

\textbf{Fixed-size Tasks are Inflexible and Inefficient.} If a programmer writes a task that consumes {\em more} energy than the device can buffer, the task will never complete using buffered energy {\em preventing forward progress} by repeatedly re-executing. If a programmer writes tasks that consume far {\em less} energy than a device can buffer, the system may operate {\em inefficiently}. When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing}---merging or dissecting multiple tasks {\em during} execution based on the program execution behavior, and {\em task downscaling}---shortening task boundaries during execution when even the smallest task does not fit the energy buffer, both models described in Section~\ref{sec:task_adaptation}, is motivated by these observations. The main enabler for task coalescing is \emph{memory virtualization} that resolves dynamic WAR dependencies, which is described in Section~\ref{sec:memory_virtulaization}.

>>>>

\textbf{Fixed-size Tasks are Inflexible and Inefficient.} If a programmer writes a task that consumes {\em more} energy than the device can buffer, the task will never complete using buffered energy {\em preventing forward progress} by repeatedly re-executing. If a programmer writes tasks that consume far {\em less} energy than a device can buffer, the system may operate {\em inefficiently}. When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing} and {\em task downscaling}.  Coalescing dynamically merges multiple tasks based on execution behavior to amortize the cost of committing each task separately. Downscaling breaks up a single task into multiple subtasks that commit individually to avoid executing a single task that is too large to complete using the device's buffered energy.  Section~\ref{sec:task_adaptation}describes \sys's adaptive coalescing and downscaling mechanisms in detail. The main enabler for \sys's adaptation is its novel \emph{memory virtualization} mechanism, which is described in Section~\ref{sec:memory_virtulaization}.
